---
title: "riotR"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
require(glue)
knitr::opts_chunk$set(echo = TRUE)
RIOT_API <- Sys.getenv("RIOT_API")
```

<!-- badges: start -->
  [![R build status](https://github.com/its-gazza/RiotR/workflows/R-CMD-check/badge.svg)](https://github.com/its-gazza/RiotR/actions)
<!-- badges: end -->

`riotR` is a API wrapper for the [Riot Games API][riot api]. Current it supports the League of Legends and Teamfight Tactics end points.  

All functions are made to mimic riot's API end point. For example, If I want to get a list of challengers in the OCE region, 
which has an end point of `/lol/league/v4/challengerleagues/by-queue/{queue}`,
you can access this end point with the following:

```{r, eval=FALSE}
challenger <- riotR::league$new(api = "YOUR API", region = "oc1")$league$challenger(queue = "RANKED_SOLO_5x5")
```

Note all additional parameter required (e.g. queue from example above) will need to be supplied

## Install
You can install `riotR` with the following:  

```{r install, eval = FALSE}
remotes::install_github("its-gazza/riotR")
```

You need an API from Riot to use this package. You can get it from [here][api key]

## Example

```{r tft example, message = FALSE, eval = FALSE}
require(riotR)

# Get a list of grandmaster players
tft <- riotR::tft$new(api = RIOT_API, region = "oc1", dry_run = FALSE)
grandmaster <- tft$league$grandmaster()
grandmaster <- httr::content(grandmaster)
grandmaster_tibble <- do.call(rbind, grandmaster$entries)
head(grandmaster_tibble)
```

Alternatively, you can specify `dry_run` to `TRUE` so all return type is the url instead of 
calling riot's API service

```{r dry run example, message = FALSE}
RIOT_API <- "YOUR_RIOT_API"
tft <- riotR::tft$new(api = RIOT_API, region = "oc1", dry_run = TRUE)
print(tft$league$grandmaster())

# Or you can call dry_run in that particular method
tft <- riotR::tft$new(api = RIOT_API, region = "oc1", dry_run = FALSE)
print(tft$league$grandmaster(dry_run = TRUE))
```


<!-- Markdown links -->
[riot api]: https://developer.riotgames.com/apis
[api key]: https://developer.riotgames.com/
